% Code

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

# Network model


```{r warning=FALSE}
library(tidyverse)
library(viridis)
library(cowplot)
library(survival)
library(gsheet)
library(ggthemes)
library(ggfortify)
library(survminer)
library(lme4)
library(metafor)
library(janitor)
library(here)
rust_sev <- read_csv("data/dat-sev.csv")
head(rust_sev)

summary(rust_sev$vi_sev)

rust_sev = rust_sev %>% 
  filter(vi_sev>0.0001)
```


```{r}


mv_sev_HCS <- rma.mv(log_sev, vi_sev,
  mods = ~brand_name,
  random = list(~brand_name | factor(study)),
  struct = "HCS",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_sev
)


mv_sev_HCS
```


## Percent control


```{r}
## HCS

efficacy_sev <- data.frame(cbind(
  (1 - exp(mv_sev_HCS$b)) * 100,
  (1 - exp(mv_sev_HCS$ci.lb)) * 100,
  (1 - exp(mv_sev_HCS$ci.ub)) * 100
))

efficacy_sev

#Organize the data.frame
efficacy_sev = efficacy_sev
names (efficacy_sev) = c("efficacy", "efficacy_up", "efficacy_lw")
  
efficacy_sev = efficacy_sev %>% 
  mutate(fungicide = c("check", "AZOX + BENZ", "BIXF + TFLX + PROT", "PICO + BENZ", "PICO + CYPR","PICO + TEBU", "PYRA + EPOX + FLUX", "TFLX + CYPR", "TFLX + PROT")) %>% 
  filter(fungicide != "check") 
efficacy_sev


#write_csv(efficacy_index, "data/efficacy_index.csv")
openxlsx::write.xlsx(efficacy_sev, here("data","efficacy_sev.xlsx"), colNames = TRUE)
```

## Contrasts

We can set linear contrasts between treatments of interest and get the P-value using the `anova` function.


```{r}
anova(mv_sev_HCS, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0, 0, 0),
  c(0, 0, 1, 0, 0, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0, 0, 0),
  c(0, 0, 0, 1, 0, 0, -1, 0, 0),
  c(0, 0, 0, 1, 0, 0, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 0, 0, 1, -1)
  ))
```


### Mods: year

```{r}
library(metafor)

mv_sev_year <- rma.mv(log_sev, vi_sev,
  mods = ~brand_name*year,
  random = list(~brand_name | factor(study)),
  struct = "HCS",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_sev %>% mutate(year= year - 2015))

mv_sev_year

anova(mv_sev_year, btt = 11:18)
```


### Decline efficacy

```{r fig.height=8, fig.width=10}

reg1 = data.frame(mv_sev_year$beta, mv_sev_year$ci.lb, mv_sev_year$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado1, into = c("lixo", "lado3"),sep = "brand_name") %>%
  select(-lixo) %>%
  filter(lado3 != "NA") %>%
  mutate(mod = c(rep("intercept", 8), rep("slope", 8))) %>% 
  select(-lado2)
names(reg1) = c("fungicide", "mean", "ci.lb", "ci.ub", "mod") 

mean = reg1 %>%
  group_by(fungicide) %>%
  select(1:2,5) %>%
  spread(mod, mean) 
names(mean) = c("fungicide", "intercept_mean", "slope_mean")

upper = reg1 %>%
  group_by(fungicide) %>%
  select(1,3,5) %>%
  spread(mod, ci.lb)
names(upper) = c("fungicide", "intercept_upper", "slope_upper")

lower = reg1 %>%
  group_by(fungicide) %>%
  select(1,4:5) %>%
  spread(mod, ci.ub)
names(lower) = c("fungicide", "intercept_lower", "slope_lower")

data_model = left_join(mean, lower, by= c("fungicide")) %>% 
  left_join(upper, by = c("fungicide"))

library(tidyverse)
rust_sev <- read_csv("data/dat-sev.csv")

sbr_effic <- rust_sev %>%
  mutate(efficacy = (1-(mean_sev/sev_check))) %>% 
  mutate(efficacy1 = efficacy*100) %>% 
  filter(brand_name!= "AACHECK")  
  

year = seq(0,6, by = 0.1) 
fungicide = NULL
year_col = NULL
for(i in 1:length(data_model$fungicide)){
data_cache = sbr_effic %>% 
    filter(brand_name == data_model$fungicide[i]) 
years = unique(data_cache$year)-2015
year = sort(years)
year = seq(first(year), last(year), by = 0.1)   
  year_col = c(year_col,year) 
  fungicide = c(fungicide, rep(data_model$fungicide[i], length(year)))
}
 

predicted = data.frame(year_col, fungicide) %>%
  mutate(year = year_col) %>%
  right_join(data_model, by = "fungicide") %>%
  mutate(mean_efficacy = (1-exp(intercept_mean + slope_mean*year))*100,
         CIL = (1-exp(intercept_lower + slope_lower*year))*100,
         CIU = (1-exp(intercept_upper + slope_upper*year))*100,
         year = year+2015) %>% 
  mutate(brand_name = fungicide) %>% 
  filter(year <2020.2) %>% 
  dplyr::select(-fungicide)
predicted

openxlsx::write.xlsx(predicted, here("data","predicted_efficacy.xlsx"), colNames = TRUE)
```


### Mods: region

```{r}
library(metafor)

rust_sev1 <- rust_sev %>% 
mutate(region = case_when(
    state == "MT" ~ "North",
    state == "BA" ~ "North",
    state == "DF" ~ "North",
    state == "MS" ~ "North",
    state == "GO" ~ "North",
    state == "TO" ~ "North",
    state == "PR" ~ "South",
    state == "MG" ~ "North",
    state == "SP" ~ "South",
    state == "RS" ~ "South")) 


rust_sev1 %>%
  group_by(study,region) %>% 
  summarise() %>% 
  tabyl(region) 

 

rust_sev1 %>%
tabyl(brand_name, region)

mv_sev_reg <- rma.mv(log_sev, vi_sev,
  mods = ~brand_name * as.factor(region),
  random = list(~brand_name | factor(study)),
  struct = "HCS",
  method = "ML",
  #control = list(optimizer = "nlm"),
  data = rust_sev1)


mv_sev_reg

anova(mv_sev_reg, btt = 11:18)
```

```{r}
reg1 = data.frame(mv_sev_reg$beta, mv_sev_reg$ci.lb, mv_sev_reg$ci.ub, mv_sev_reg$se) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lixo","lado3"),sep = "region" ) %>% 
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "brand_name") %>%
  select(-lixo) %>%
  filter(lado1 != "NA") %>%
  mutate(n = seq(1:16))
names(reg1) = c("fungicide", "region", "mean_log", "ci.lb_log", "ci.ub_log", "SE_eff","n") 

reg2 = reg1 %>% 
  filter(n < 9) %>% 
  mutate(region = rep("North", length(fungicide)))

reg3 = reg1 %>% 
  filter(n > 8) %>% 
  mutate(region = rep("South", length(fungicide)))

reg4 = rbind(reg2,reg3) %>% 
  select(-"n")

openxlsx::write.xlsx(reg4, here("data","eff_log_region.xlsx"), colNames = TRUE)
```


#### Region effect


```{r}
reg1 = data.frame(mv_sev_reg$beta, mv_sev_reg$ci.lb, mv_sev_reg$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lixo","lado3"),sep = "region" ) %>% 
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "brand_name") %>%
  select(-lixo) %>%
  filter(lado1 != "NA") %>%
  mutate(n = seq(1:16))
names(reg1) = c("fungicide", "region", "mean", "ci.lb", "ci.ub", "n") 

reg2 = reg1 %>% 
  filter(n < 9) %>% 
  mutate(region = rep("North", length(fungicide)))

reg3 = reg1 %>% 
  filter(n > 8) %>% 
  mutate(region = rep("South", length(fungicide)))

reg4 = rbind(reg2,reg3)  

mean = reg4%>% 
  group_by(fungicide) %>% 
  select(1:3) %>% 
  spread(region, mean) %>% 
  mutate(mean = (1-exp((North + South)))*100) %>% 
  select(1,4)

upper = reg4%>% 
  group_by(fungicide) %>% 
  select(1,2,4) %>% 
  spread(region, ci.lb) %>% 
  mutate(upper = (1-exp((North + South)))*100) %>%  
  select(1,4)

lower = reg4%>% 
  group_by(fungicide) %>% 
  select(1,2,5) %>% 
  spread(region, ci.ub) %>% 
  mutate(lower = (1-exp((North + South)))*100) %>% 
  select(1,4)

reg5 = left_join(mean, lower, by= c("fungicide")) %>% 
  left_join(upper, by = c("fungicide")) %>% 
  mutate(region = rep("South", length("fungicide"))) %>% 
  select("fungicide", "region", "mean", "lower", "upper")


North = reg4 %>% 
  filter(region == "North") %>% 
  select(1:5) %>% 
  group_by(fungicide, region) %>%
  summarise(mean = (1-exp(mean))*100,
            lower = (1-exp(ci.ub))*100,
            upper = (1-exp(ci.lb))*100)
names(North) = c("fungicide", "region", "mean", "lower", "upper") 


reg6 = full_join(North,reg5)
reg6

openxlsx::write.xlsx(reg6, here("data","eff_region.xlsx"), colNames = TRUE)
```


### Inconsistency

We used a factorial-type ANOVA model to determine the significance of the *treatment x design* interaction, evaluated based on the Wald test statistic.


```{r}
mv_sev_design <- rma.mv(log_sev, vi_sev,
  mods = ~brand_name * design,
  random = list(~ 1 | study / design / brand_name),
  struct = "HCS",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_sev)

mv_sev_design

anova(mv_sev_design, btt = 11:18)

```
