% Code

# Data


```{r, warning=FALSE}
library(readr)
library(metafor)
library(tidyverse)
library(here)
rust_yld <- read_csv("data/dat-yld.csv")

```



## Absolute yield

```{r}

library(metafor)

mv_yld <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name,
  random = list(~brand_name | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld
)

summary(mv_yld)
```


```{r}
yield_res<- data.frame(cbind(mv_yld$b, 
                             mv_yld$ci.lb,
                             mv_yld$ci.ub)) %>% 
  mutate(fungicide = c("check", "AZOX + BENZ", "BIXF + TFLX + PROT", "PICO + BENZ", "PICO + CYPR","PICO + TEBU", "PYRA + EPOX + FLUX", "TFLX + CYPR", "TFLX + PROT")) %>% 
  filter(fungicide != "check")


names (yield_res) = c("yld", "yld_lower", "yld_upper", "fungicide")
  
yield_res


#write_csv(yield_res, "data/yld_kg.csv")
openxlsx::write.xlsx(yield_res, here("data","yld_kg.xlsx"), colNames = TRUE)
```

### Contrasts

We can set linear contrasts between treatments of interest and get the P-valued using the `anova` function.

```{r}
anova(mv_yld, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0, 0, 0),
  c(0, 0, 1, 0, 0, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0, 0, 0),
  c(0, 0, 0, 1, 0, 0, -1, 0, 0),
  c(0, 0, 0, 1, 0, 0, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 0, 0, 1, -1)
  ))
```

## Moderator analysis

### Mods: year 

```{r, warning=FALSE}
mv_yld_year <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name * as.numeric(year),
  random = list(~brand_name | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld %>% mutate(year= year - 2015))

mv_yld_year

anova(mv_yld_year, btt = 11:18)
```

#### Decline yield

```{r fig.height=8, fig.width=10}

yld_gain <- rust_yld %>%
  mutate(gain = mean_yld - yld_check) %>% 
  filter(brand_name!= "AACHECK")  
  

yld_gain <- yld_gain %>% 
mutate(region = case_when(
    state == "MT" ~ "North",
    state == "BA" ~ "North",
    state == "DF" ~ "North",
    state == "MS" ~ "North",
    state == "GO" ~ "North",
    state == "TO" ~ "North",
    state == "PR" ~ "South",
    state == "MG" ~ "South",
    state == "SP" ~ "South",
    state == "RS" ~ "South")) 


reg1 = data.frame(mv_yld_year$beta, mv_yld_year$ci.lb, mv_yld_year$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado1, into = c("lixo", "lado3"),sep = "brand_name") %>%
  select(-lixo) %>%
  filter(lado3 != "NA") %>%
  mutate(mod = c(rep("intercept", 8), rep("slope", 8))) %>% 
  select(-lado2)
names(reg1) = c("fungicide", "mean", "ci.lb", "ci.ub", "mod") 

mean = reg1 %>%
  group_by(fungicide) %>%
  select(1:2,5) %>%
  spread(mod, mean) 
names(mean) = c("fungicide", "intercept_mean", "slope_mean")

upper = reg1 %>%
  group_by(fungicide) %>%
  select(1,3,5) %>%
  spread(mod, ci.lb)
names(upper) = c("fungicide", "intercept_upper", "slope_upper")

lower = reg1 %>%
  group_by(fungicide) %>%
  select(1,4:5) %>%
  spread(mod, ci.ub)
names(lower) = c("fungicide", "intercept_lower", "slope_lower")

data_model = left_join(mean, lower, by= c("fungicide")) %>% 
  left_join(upper, by = c("fungicide"))

year = seq(0,6, by = 0.1) 
fungicide = NULL
year_col = NULL
for(i in 1:length(data_model$fungicide)){
data_cache = yld_gain %>% 
    filter(brand_name == data_model$fungicide[i]) 
years = unique(data_cache$year)-2015
year = sort(years)
year = seq(first(year), last(year), by = 0.1)   
  year_col = c(year_col,year) 
  fungicide = c(fungicide, rep(data_model$fungicide[i], length(year)))
}
 
predicted = data.frame(year_col, fungicide) %>%
  mutate(year = year_col) %>%
  right_join(data_model, by = "fungicide") %>%
  mutate(mean_gain = intercept_mean + slope_mean*year,
         CIL = intercept_lower + slope_lower*year,
         CIU = intercept_upper + slope_upper*year,
         year = year+2015) %>% 
  mutate(brand_name = fungicide) %>% 
  filter(year <2020.2) %>% 
  dplyr::select(-fungicide)
predicted

openxlsx::write.xlsx(predicted, here("data","predicted_yield.xlsx"), colNames = TRUE)
```


### AZOX + BENZ

```{r}
library(janitor)
# create the log of the sev variable
rust_yld1 <- rust_yld %>%
  filter(brand_name %in% c("AACHECK", "AZOX + BENZ")) %>% 
  group_by(study) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

rust_yld1 = rust_yld1 %>% 
mutate(region = case_when(
    state == "MT" ~ "North",
    state == "BA" ~ "North",
    state == "DF" ~ "North",
    state == "MS" ~ "North",
    state == "GO" ~ "North",
    state == "TO" ~ "North",
    state == "PR" ~ "South",
    state == "MG" ~ "North",
    state == "SP" ~ "South",
    state == "RS" ~ "South")) 

rust_yld1 %>%
tabyl(brand_name, region)

rust_yld1 %>%
tabyl(brand_name, state)

```


#### NW

```{r}
library(metafor)
yld_gain <- rust_yld %>%
  mutate(gain = mean_yld - yld_check) %>% 
  filter(brand_name!= "AACHECK")  

rust_yld_nor <- rust_yld1 %>% 
filter(region == "North")

mv_yld_year <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name * as.numeric(year),
  random = list(~brand_name | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld_nor %>% mutate(year= year - 2015))

mv_yld_year


reg1 = data.frame(mv_yld_year$beta, mv_yld_year$ci.lb, mv_yld_year$ci.ub, mv_yld_year$se) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado1, into = c("lixo", "lado3"),sep = "brand_name") %>%
  select(-lixo) %>%
  filter(lado3 != "NA") %>%
  mutate(mod = c(rep("intercept", 1), rep("slope", 1))) %>% 
  mutate(region = rep("North", length(mod))) %>% 
  select(-lado2) 
names(reg1) = c("fungicide", "mean", "ci.lb", "ci.ub", "SE", "mod", "region") 

elatus_norte = reg1


```

#### SE

```{r}
library(metafor)
yld_gain <- rust_yld %>%
  mutate(gain = mean_yld - yld_check) %>% 
  filter(brand_name!= "AACHECK")  

rust_yld_south <- rust_yld1 %>% 
filter(region == "South")

mv_yld_year <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name * as.numeric(year),
  random = list(~brand_name | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld_south %>% mutate(year= year - 2015))

mv_yld_year


reg1 = data.frame(mv_yld_year$beta, mv_yld_year$ci.lb, mv_yld_year$ci.ub, mv_yld_year$se) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado1, into = c("lixo", "lado3"),sep = "brand_name") %>%
  select(-lixo) %>%
  filter(lado3 != "NA") %>%
  mutate(mod = c(rep("intercept", 1), rep("slope", 1))) %>% 
  mutate(region = rep("South", length(mod))) %>% 
  select(-lado2) 
names(reg1) = c("fungicide", "mean", "ci.lb", "ci.ub", "SE", "mod", "region") 

elatus_sul = reg1



```


### PICO + BENZ

```{r}
library(janitor)
# create the log of the sev variable
rust_yld1 <- rust_yld %>%
  filter(brand_name %in% c("AACHECK", "PICO + BENZ")) %>% 
  group_by(study) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

rust_yld1 = rust_yld1 %>% 
mutate(region = case_when(
    state == "MT" ~ "North",
    state == "BA" ~ "North",
    state == "DF" ~ "North",
    state == "MS" ~ "North",
    state == "GO" ~ "North",
    state == "TO" ~ "North",
    state == "PR" ~ "South",
    state == "MG" ~ "North",
    state == "SP" ~ "South",
    state == "RS" ~ "South")) 

rust_yld1 %>%
tabyl(brand_name, region)

rust_yld1 %>%
tabyl(brand_name, state)

```


#### NW

```{r}
library(metafor)
yld_gain <- rust_yld %>%
  mutate(gain = mean_yld - yld_check) %>% 
  filter(brand_name!= "AACHECK")  

rust_yld_nor <- rust_yld1 %>% 
filter(region == "North")

mv_yld_year <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name * as.numeric(year),
  random = list(~brand_name | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld_nor %>% mutate(year= year - 2015))

mv_yld_year


reg1 = data.frame(mv_yld_year$beta, mv_yld_year$ci.lb, mv_yld_year$ci.ub, mv_yld_year$se) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado1, into = c("lixo", "lado3"),sep = "brand_name") %>%
  select(-lixo) %>%
  filter(lado3 != "NA") %>%
  mutate(mod = c(rep("intercept", 1), rep("slope", 1))) %>% 
  mutate(region = rep("North", length(mod))) %>% 
  select(-lado2) 
names(reg1) = c("fungicide", "mean", "ci.lb", "ci.ub", "SE", "mod", "region") 

vess_norte = reg1 




```

#### SE

```{r}
library(metafor)
yld_gain <- rust_yld %>%
  mutate(gain = mean_yld - yld_check) %>% 
  filter(brand_name!= "AACHECK")  

rust_yld_south <- rust_yld1 %>% 
filter(region == "South")

mv_yld_year <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name * as.numeric(year),
  random = list(~brand_name | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld_south %>% mutate(year= year - 2015))

mv_yld_year


reg1 = data.frame(mv_yld_year$beta, mv_yld_year$ci.lb, mv_yld_year$ci.ub, mv_yld_year$se) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado1, into = c("lixo", "lado3"),sep = "brand_name") %>%
  select(-lixo) %>%
  filter(lado3 != "NA") %>%
  mutate(mod = c(rep("intercept", 1), rep("slope", 1))) %>% 
  mutate(region = rep("South", length(mod))) %>% 
  select(-lado2) 
names(reg1) = c("fungicide", "mean", "ci.lb", "ci.ub", "SE", "mod", "region") 

vess_sul = reg1 

data_two_fung = rbind(elatus_norte, elatus_sul, vess_norte, vess_sul)

openxlsx::write.xlsx(data_two_fung, here("data","Elatus_Vessarya_yld_simulation.xlsx"), colNames = TRUE)



```

### Mods: region 

```{r, warning=FALSE}
rust_yld1 = rust_yld %>% 
mutate(region = case_when(
    state == "MT" ~ "North",
    state == "BA" ~ "North",
    state == "DF" ~ "North",
    state == "MS" ~ "North",
    state == "GO" ~ "North",
    state == "TO" ~ "North",
    state == "PR" ~ "South",
    state == "MG" ~ "North",
    state == "SP" ~ "South",
    state == "RS" ~ "South")) 

rust_yld1 %>%
tabyl(brand_name, region)

mv_yld_region <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name * as.factor(region),
  random = list(~factor(brand_name) | factor(study)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld1)

mv_yld_region

anova(mv_yld_region, btt = 11:18)
```

```{r}
reg1 = data.frame(mv_yld_region$beta, mv_yld_region$ci.lb, mv_yld_region$ci.ub, mv_yld_region$se) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lixo","lado3"),sep = "region") %>% 
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "brand_name" ) %>%
  select(-lixo) %>%
  filter(lado1 != "NA") %>%
  mutate(n = seq(1:16))
names(reg1) = c("fungicide", "region", "mean_yld", "ci.lb_yld", "ci.ub_yld", "SE_yld","n") 

reg2 = reg1 %>% 
  filter(n < 9) %>% 
  mutate(region = rep("North", length(fungicide)))

reg3 = reg1 %>% 
  filter(n > 8) %>% 
  mutate(region = rep("South", length(fungicide)))

reg4 = rbind(reg2,reg3) %>% 
  select(-"n")


openxlsx::write.xlsx(reg4, here("data","yld_SE_region.xlsx"), colNames = TRUE)


```


```{r}
eff_log = read_excel("data/eff_log_region.xlsx")
yld_reg <- read_excel("data/yld_SE_region.xlsx")

data_simulation = full_join(eff_log, yld_reg, by = c("fungicide", "region"))
openxlsx::write.xlsx(data_simulation, here("data","data_simulation.xlsx"), colNames = TRUE)

```


#### Mod effect

```{r}
reg1 = data.frame(mv_yld_region$beta, mv_yld_region$ci.lb, mv_yld_region$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lixo","lado3"),sep = "region") %>% 
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "brand_name" ) %>%
  select(-lixo) %>%
  filter(lado1 != "NA") %>%
  mutate(n = seq(1:16))
names(reg1) = c("fungicide", "class", "mean", "ci.lb", "ci.ub", "n") 

reg2 = reg1 %>% 
  filter(n < 9) %>% 
  mutate(class = rep("North", length(fungicide)))

reg3 = reg1 %>% 
  filter(n > 8) %>% 
  mutate(class = rep("South", length(fungicide)))

reg4 = rbind(reg2,reg3)  

mean = reg4%>% 
  group_by(fungicide) %>% 
  select(1:3) %>% 
  spread(class, mean) %>% 
  mutate(mean = North + South) %>% 
  select(1,4)

lower = reg4%>% 
  group_by(fungicide) %>% 
  select(1,2,4) %>% 
  spread(class, ci.lb) %>% 
  mutate(lower = North + South) %>%  
  select(1,4)

upper = reg4%>% 
  group_by(fungicide) %>% 
  select(1,2,5) %>% 
  spread(class, ci.ub) %>% 
  mutate(upper = North + South) %>% 
  select(1,4)

reg5 = left_join(mean, lower, by= c("fungicide")) %>% 
  left_join(upper, by = c("fungicide")) %>% 
  mutate(class = rep("South", length("fungicide"))) %>% 
  select("fungicide", "class", "mean", "lower", "upper")


North = reg4 %>% 
  filter(class == "North") %>% 
  select(1:5)
names(North) = c("fungicide", "class", "mean", "lower", "upper") 

reg6 = full_join(North,reg5)
reg6

openxlsx::write.xlsx(reg6, here("data","yld_region.xlsx"), colNames = TRUE)
```

### Mods: severity baseline 


```{r, warning=FALSE}
library(tidyverse)

rust_yld <- rust_yld %>%
    mutate(
    sev_check_class = case_when(
      sev_check < 70 ~ "Low",
      sev_check >= 70 ~ "High"))

rust_yld %>%
tabyl(brand_name, sev_check_class)

mv_yld_sev_class <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name * as.factor(sev_check_class) ,
  random = list(~factor(brand_name) | factor(study)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld)

mv_yld_sev_class

anova(mv_yld_sev_class, btt = 11:18)
```

#### Mod effect

```{r}
reg1 = data.frame(mv_yld_sev_class$beta, mv_yld_sev_class$ci.lb, mv_yld_sev_class$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lixo","lado3"),sep = "sev_check_class") %>% 
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "brand_name" ) %>%
  select(-lixo) %>%
  filter(lado1 != "NA") %>%
  mutate(n = seq(1:16))
names(reg1) = c("fungicide", "class", "mean", "ci.lb", "ci.ub", "n") 

reg2 = reg1 %>%
  filter(n < 9) %>% 
  mutate(class = rep("High", length(fungicide)))

reg3 = reg1 %>% 
  filter(n > 8) %>% 
  mutate(class = rep("Low", length(fungicide)))

reg4 = rbind(reg2,reg3)  

mean = reg4%>% 
  group_by(fungicide) %>% 
  select(1:3) %>% 
  spread(class, mean) %>% 
  mutate(mean = High + Low) %>% 
  select(1,4)

lower = reg4%>% 
  group_by(fungicide) %>% 
  select(1,2,4) %>% 
  spread(class, ci.lb) %>% 
  mutate(lower = High + Low) %>%  
  select(1,4)

upper = reg4%>% 
  group_by(fungicide) %>% 
  select(1,2,5) %>% 
  spread(class, ci.ub) %>% 
  mutate(upper = High + Low) %>% 
  select(1,4)

reg5 = left_join(mean, lower, by= c("fungicide")) %>% 
  left_join(upper, by = c("fungicide")) %>% 
  mutate(class = rep("Low", length("fungicide"))) %>% 
  select("fungicide", "class", "mean", "lower", "upper")


High = reg4 %>% 
  filter(class == "High") %>% 
  select(1:5)
names(High) = c("fungicide", "class", "mean", "lower", "upper") 

reg6 = full_join(High,reg5)
reg6

openxlsx::write.xlsx(reg6, here("data","yld_baseline.xlsx"), colNames = TRUE)
```


### Inconsistency

We used a factorial-type ANOVA model to determine the significance of the *treatment x design* interaction, evaluated based on the Wald test statistic.

```{r}
mv_yld_design <- rma.mv(mean_yld, vi_yld,
  mods = ~brand_name * design,
  random = list(~ 1 | study / design / brand_name),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = rust_yld)

mv_yld_design

anova(mv_yld_design, btt = 11:18)
```

