


# Raw Data import 


```{r, warning=FALSE}
library(tidyverse)
library(metafor)
library(ggthemes)
library(cowplot)
library(scales)
library(broom)
library(dplyr)
library(readxl)
library(gsheet)
library(janitor)
library(cowplot)


rust <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Xx_gK6ERLLhQGIrOPB_ZYs9LoHTmsv030s30Dc_TPzg/edit#gid=287066174", sheetid = "2015-2020")


rust %>% 
  group_by(study)
length(unique(rust$study))
```



## Summarrising data (mean and variance)

```{r, warning=FALSE}

rust1 <- rust %>% 
  group_by(study, year, location, state, n_spray, brand_name) %>% 
  summarise(mean_sev = mean(sev),
            mean_yld = mean(yld))

rust_sev <- rust %>% 
  group_by(study, year) %>%  
  select(brand_name, rep, sev) %>%
  group_by(study, year) %>% 
  do(tidy(aov(.$sev ~ .$brand_name + factor(.$rep)))) %>% 
  filter(term == "Residuals") %>% 
  select(1,2,6) %>% 
  set_names(c("study", "year", "v_sev"))


rust_yld <- rust %>% 
  filter(yld>0) %>% 
  group_by(study, year) %>% 
  select(brand_name, rep, yld) %>% 
  group_by(study, year) %>% 
  do(tidy(aov(.$yld ~ .$brand_name + factor(.$rep)))) %>% 
  filter(term == "Residuals") %>% 
  select(1,2,6) %>% 
  set_names(c("study", "year", "v_yld"))


qmr = left_join(rust_sev, rust_yld)

rust_trial = full_join(rust1, qmr)
rust_trial
```


## Exploratory analysis

### By year

```{r}
library(janitor) 
a1 = rust_trial %>%
  group_by(study,year) %>% 
  summarise() %>% 
  tabyl(year)
a1
```

### By year and n_spray

```{r}
library(janitor) 
a1 = rust_trial %>%
  group_by(study,year,n_spray) %>% 
  summarise() %>%
  tabyl(n_spray, year)
a1
```

### By location

```{r}
rust_trial %>%
  group_by(study,location) %>% 
  summarise() %>%
  tabyl(location)
 

rust %>% 
  group_by(location)
length(unique(rust$location))
```


### By state

```{r}
a2 = rust_trial %>%
  group_by(study,state) %>% 
  summarise() %>% 
  tabyl(state)
a2
```

### By active ingredient

```{r}
a3 = rust_trial %>%
  group_by(study,brand_name) %>% 
  summarise() %>% 
  tabyl(brand_name) %>% 
  filter(n>100)
a3
```

### By active ingredient and year

```{r}
rust_trial %>%
  tabyl(brand_name,year)
```
### By active ingredient and n_spray

```{r}
rust_trial %>%
  tabyl(brand_name,n_spray)
```

## Selected Fungicides

```{r, warning=FALSE}

rust3 <- rust_trial %>% 
  filter(brand_name %in% c("CHECK", "Aproach Prima", "Ativum", "Elatus", "FOX", "FOX Xpro", "Horos", "SphereMax", "Vessarya")) 


rust3 %>%
  tabyl(brand_name, year)

# Renaming the treatments 
library(plyr)
rust3$brand_name <- revalue(rust3$brand_name, c("CHECK" = "AACHECK"))
rust3$brand_name <- revalue(rust3$brand_name, c("FOX" = "TFLX + PROT"))
rust3$brand_name <- revalue(rust3$brand_name, c("FOX Xpro" = "BIXF + TFLX + PROT"))
rust3$brand_name <- revalue(rust3$brand_name, c("Horos" = "PICO + TEBU"))
rust3$brand_name <- revalue(rust3$brand_name, c("SphereMax" = "TFLX + CYPR"))
rust3$brand_name <- revalue(rust3$brand_name, c("Ativum" = "PYRA + EPOX + FLUX"))
rust3$brand_name <- revalue(rust3$brand_name, c("Elatus" = "AZOX + BENZ"))
rust3$brand_name <- revalue(rust3$brand_name, c("Vessarya" = "PICO + BENZ"))
rust3$brand_name <- revalue(rust3$brand_name, c("Aproach Prima" = "PICO + CYPR"))
detach("package:plyr", unload = TRUE)



```


## Check columns 

```{r, warning=FALSE}
# these two columns will be used as moderator variables later
sbr_check = rust3 %>% 
  ungroup() %>% 
  filter(brand_name == "AACHECK")  %>% 
  mutate(check = brand_name, sev_check = mean_sev, v_sev_check = v_sev, yld_check = mean_yld, v_yld_check = v_yld ) %>% 
  select(study, yld_check, v_yld_check, sev_check, v_sev_check)

sbr_data = rust3 %>% 
  full_join(sbr_check)

```

# Create datasets


## Severity Index 

```{r}
rust_sev <- sbr_data %>% 
  filter(mean_sev != "NA") %>% 
  filter(mean_sev>0)

hist(rust_sev$mean_sev)


# create the log of the sev variable
rust_sev <- rust_sev %>%
  mutate(log_sev = log(mean_sev))
hist(rust_sev$log_sev)


# create the sampling variance for the log of sev
rust_sev$vi_sev <- with(rust_sev, v_sev / (4 * mean_sev^2))

summary(rust_sev$vi_sev)
 
rust_sev <- rust_sev %>%
  group_by(study) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

```

### Design groups

```{r}
rust_sev1 = rust_sev %>% 
  group_by(study) %>% 
  summarise(brand_name1=paste(brand_name, collapse=';')) 

rust_sev1 %>% 
  tabyl(brand_name1)
```


Ten different designs (here design refers to the set of treatments in the trial) were found in the trials reporting SBR severity.

```{r}
design1 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(1, length(brand_name))) %>% 
  filter(n2 == 9) %>% 
  filter(n3 == 9)
design1

design2 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(2, length(brand_name))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design2

design3 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "BIXF + TFLX + PROT", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(3, length(brand_name))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design3

design4 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "TFLX + PROT", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(4, length(brand_name))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design4

design5 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(5, length(brand_name))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design5

design6 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(6, length(brand_name))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design6

design7 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(7, length(brand_name))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design7

design8 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "PICO + TEBU", "TFLX + CYPR")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(8, length(brand_name))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design8

design9 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "PICO + TEBU")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(9, length(brand_name))) %>% 
  filter(n2 == 5) %>% 
  filter(n3 == 5)
design9

design10 = rust_sev %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "AZOX + BENZ", "PICO + TEBU")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(10, length(brand_name))) %>% 
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design10

sbr_sev_design = rbind(design1, design2, design3, design4, design5, design6, design7, design8, design9, design10)


sbr_sev_design %>% 
  group_by(study,design) %>% 
  summarize() %>% 
  tabyl(design)
```


```{r}

library(readr)
write_csv(sbr_sev_design, "data/dat-sev.csv")


library(knitr)
library(tidyverse)
rust_sev <- read_csv("data/dat-sev.csv")

rust_sev %>% 
  group_by(study)
length(unique(rust_sev$study))

rust_sev %>% 
tabyl(state)

length(unique(rust_sev$study))


summary(rust_sev$sev_check)


median = rust_sev %>% 
  group_by(study, year, brand_name) %>% 
  filter(brand_name == "AACHECK") %>% 
  summarise(median = median(sev_check)) %>% 
  filter(median>60)

length(unique(median$study))
```



```{r}
rust_sev %>%
  tabyl(brand_name, year)

rust_sev %>%
  tabyl(brand_name)
```




## Yield

```{r}
rust_yld <- sbr_data %>% 
  filter(mean_yld != "NA")

# Sampling variance for yield
rust_yld$vi_yld <- with(rust_yld, v_yld/4) # multivariate approach

rust_yld <- rust_yld %>%
  group_by(study) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

```


### Design groups

```{r}
rust_yld1 = rust_yld %>% 
  group_by(study) %>% 
  summarise(brand_name1=paste(brand_name, collapse=';')) 

rust_yld1 %>% 
  tabyl(brand_name1)
```


Ten different designs (here design refers to the set of treatments in the trial) were found in the trials reporting soybean yield.

```{r}
design1 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(1, length(brand_name))) %>% 
  filter(n2 == 9) %>% 
  filter(n3 == 9)
design1

design2 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(2, length(brand_name))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design2

design3 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "BIXF + TFLX + PROT", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(3, length(brand_name))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design3

design4 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "TFLX + PROT", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(4, length(brand_name))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design4

design5 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(5, length(brand_name))) %>% 
  filter(n2 == 8) %>% 
  filter(n3 == 8)
design5

design6 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(6, length(brand_name))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design6

design7 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "BIXF + TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(7, length(brand_name))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design7

design8 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "PICO + TEBU", "TFLX + CYPR")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(8, length(brand_name))) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design8

design9 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "AACHECK", "AZOX + BENZ", "TFLX + PROT", "PICO + TEBU")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(9, length(brand_name))) %>% 
  filter(n2 == 5) %>% 
  filter(n3 == 5)
design9

design10 = rust_yld %>% 
  group_by(study) %>% 
  filter(brand_name  %in% c("PICO + CYPR", "PYRA + EPOX + FLUX", "AACHECK", "TFLX + PROT", "PICO + TEBU", "TFLX + CYPR", "PICO + BENZ")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(10, length(brand_name))) %>% 
  filter(n2 == 7) %>% 
  filter(n3 == 7)
design10

sbr_yld_design = rbind(design1, design2, design3, design4, design5, design6, design7, design8, design9, design10)


sbr_yld_design %>% 
  group_by(study,design) %>% 
  summarize() %>% 
  tabyl(design)
```


```{r}
library(readr)
write_csv(sbr_yld_design, "data/dat-yld.csv")


library(readr)
library(tidyverse)
rust_yld <- read_csv("data/dat-yld.csv")
rust_yld %>% 
  group_by(study)
length(unique(rust_yld$study))

rust_yld %>% 
  group_by(study, n2) %>%
  summarise() %>% 
  tabyl(n2)

yld_year = rust_yld %>% 
  filter(brand_name == "AACHECK") %>% 
  filter(year == 2020)

summary(yld_year$yld_check)
```




```{r}
rust_yld %>%
  tabyl(brand_name, year)

rust_yld %>%
  tabyl(brand_name)
```


